Study Comparison

### 2024-02-16 analysis/study_comaprison.Rmd
revisions

vl_saliva_pl <- vl_saliva %>%
  ggplot(aes(x = virus_type, y = ct)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(shape = year, color = virus), width = .25, height = 0) +
  ggsignif::geom_signif(
    annotations = paste0("p=", round(vl_test$p.value, 2)), 
    y_position = 44, 
    xmin = 1, xmax = 2, 
    textsize = 8 / cm(1), 
    vjust = -.5, 
    tip_length = .075) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_shape_manual(values = c(1, 17)) +
  scale_y_continuous(limits = c(NA, 46)) +
  labs(y = "Ct value") +
  theme_bw2() +
  theme(axis.title.x = element_blank(),
        legend.position = c(0.1, 0.87),
        legend.background = element_rect(color = "black"),
        plot.title.position = "plot",
        legend.title = element_blank()) +
  guides(color = "none")

save_plot(vl_saliva_pl,
          "../results/comparison-viral-loads.png",
          w = 12, h = 8)
```

>>>>

vl_saliva_pl <- vl_saliva %>%
  ggplot(aes(x = virus_type, y = ct)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(shape = year, color = virus), width = .25, height = 0) +
  ggsignif::geom_signif(
    annotations = paste0("p=", round(vl_test$p.value, 2)), 
    y_position = 44, 
    xmin = 1, xmax = 2, 
    textsize = 8 / cm(1), 
    vjust = -.5, 
    tip_length = .075) +
  scale_color_manual(values = wes_palette("IsleofDogs1")) +
  scale_shape_manual(values = c(1, 17)) +
  scale_y_continuous(limits = c(NA, 46)) +
  labs(y = "Ct value") +
  theme_bw2() +
  theme(axis.title.x = element_blank(),
        legend.position = "top",
        plot.title.position = "plot",
        legend.title = element_blank()) +
  guides(color = guide_legend(nrow = 2))

save_plot(vl_saliva_pl,
          "../results/comparison-viral-loads.png",
          w = 10, h = 12)
```
